The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
remove addressed comments

The parametric redshift distributions that we use are
\begin{equation}\label{E:pz1}
 p_1(z) \propto z^{a-1}\exp\left[{-bz}\right]
\end{equation}
and 
\begin{equation}\label{E:pz2}
 p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
\end{equation}
the latter of which was first presented by
\cite{Redshift_modelling}. Here $a$, $b$, and
$z_0$ are free parameters that are to be determined.  The
normalization constants depend not only on the parameters but also on
the lower and the upper limit of the redshifts considered, where we
fix the normalization to ensure that the predicted number of galaxies
in the range used ($0.3<z<1$) is equal to the actual number. 
Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
histogram together with the best-fitting parametric distributions.
\rachel{The results for the 2nd redshift distribution do not look that
  great.  Does it help if we go to $z<1.25$?  I thought the photo-$z$
  were okay in that regime, and it's only beyond $1.25$ that they get
  really scary.  We could use up to $1.25$ for determining the
  redshift distribution, even if we're only trying to find
  overdensities for $z<1$.}

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3 - 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
     The green vertical dotted line represents our luminosity cut. \rachel{What redshift range?}\arun{addressed.}} 
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of absolute magnitude $M_I$ for various
     flux-limited samples in the redshift range $[0.80 - 0.85]$ are plotted together. The vertical line
     corresponds to our luminosity cut of $-20.8$, brighter than which
     the $m_\text{F814W}<23.5$ sample includes $>95.3$ per cent of the
     galaxies in the $m_\text{F814W}<25.2$ sample.
   \rachel{Is this plot and the numbers in the caption for
     $0.8<z<0.85$ only?  This is currently implied by the text.  If
     that is true, then please fix the figure and caption to say
     this.  If that is wrong, then please fix the text.} \arun{Text is correct. Caption fixed.}}
   \label{fig:MIhist}
 \end{figure}

>>>>

The parametric redshift distributions that we use are
\begin{equation}\label{E:pz1}
 p_1(z) \propto z^{a-1}\exp\left[{-bz}\right]
\end{equation}
and 
\begin{equation}\label{E:pz2}
 p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
\end{equation}
the latter of which was first presented by
\cite{Redshift_modelling}. Here $a$, $b$, and
$z_0$ are free parameters that are to be determined.  The
normalization constants depend not only on the parameters but also on
the lower and the upper limit of the redshifts considered, where we
fix the normalization to ensure that the predicted number of galaxies
in the range used ($0.3<z<1$) is equal to the actual number. 
Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
histogram together with the best-fitting parametric distributions.
\rachel{New suggestion re: 2nd redshift distribution: it just looks so
  bad, I worry that this functional form is simply wrong 
  and we should use something newer that has been shown to work with
  modern redshift surveys.  Let me suggest something you can
  do as an immediate sanity check.   Look at
  \cite{2004ApJ...617..765C} table 4, which gives parametrized fits to
  the redshift distribution from DEEP2 for samples binned by
  $R_\text{AB}$ and $I_\text{AB}$.  Use the results for the
  $18<I_\text{AB}<23$ bin and the $18<I_\text{AB}<24$ bin,
  interpolating linearly between them since your sample is limited at
  $23.5$.  Their results suggest that either $z^2 \exp{[-z/0.262]}$ or
  $z^2 \exp{[-(z/0.361)^{1.2}]}$ should be decent descriptions of your sample.  Just as a quick
  sanity check can you please plot those  distributions (appropriately
  normalized) on top of what you have in the top panel of figure 1,
  and see how they look?  If they look OK, then I would be inclined to
  completely eliminate the 2nd distribution, and just use the 1st one
  that you're fitting and one of the ones from Coil as your way of
  checking overdensities and underdensities.
}

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
     The green vertical dotted line represents our luminosity cut. } 
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of absolute magnitude $M_I$ for various
     flux-limited samples in the redshift range $[0.80, 0.85]$ are plotted together. The vertical line
     corresponds to our luminosity cut of $-20.8$, brighter than which
     the $m_\text{F814W}<23.5$ sample includes $>95.3$ per cent of the
     galaxies in the $m_\text{F814W}<25.2$ sample.
   }
   \label{fig:MIhist}
 \end{figure}
